\documentclass[paper=letter,fontsize=10pt]{article}
\usepackage{newcent}
\usepackage{lineno}
\usepackage{enumitem}
\title{\textsc{\textit{Bronner v. Olympus} Issue 1 Summary}}
\newcommand{\case}[3]{\noindent {\large\textbf{\textit{#1}, #2 (#3)}} \par}
\newcommand{\inv}[3]{\noindent \textbf{#1} \\ \noindent \textit{#2} \begin{quote} #3 \end{quote} \par}
\date{}
\author{\textit{Varun Iyer} \hspace{.5em} $\cdot$ \hspace{.5em} \textit{July 14, 2019}}
\begin{document}
\maketitle
\inv{Warrant 1}{March 17, 2015} {
	Issued against Olympus Cellular to disclose to disclose Robert DeNolf’s telephone records for the past three months.
}
\inv{Warrant 2}{June 18, 2015} {
	Repeated a 3-month warrant of DeNolf’s telephone records. Discovered that they were using burner phones.
}
\inv{Warrant 3}{July 19, 2015} {
	Every phone number that texted or called DeNolf for the prior month from Olympus Cellular.
	Burner phones from Warrants 1 and 2 no longer being used for criminal activity.
}
\inv{Warrant 4}{August 20, 2015} {
	Every number that called or texted DeNolf’s burner phone more than five times during the immediately preceding three months. From Olumpus Cellular.
	One of the numbers was recognized by informant as Bobby Bronner’s; his involvement in human trafficking was unknown.
	He frequented a bar as well as a restaurant owned by friends of DeNolf.
}
\inv{Internet Research}{February 6, 2016} {
	Backpage.com had ad for ‘Super Bowl Specials’, none of these ads included phone numbers associated with DeNolf.
	However, two ads instructed clients to ask for ‘B.B.’.
}
\inv{Warrant 5}{January 2, 2016} {
	Every phone number that texted or called Bronner or DeNolf’s burner phones more than five times in the preceding three months. In December, Bronner communicated with ten burner numbers associated with DeNolf’s phone that were identified in the Data collected on July 19, 2015.
	This led investigator’s to focus on Bronner’s phone.
}
\inv{Warrantless Investigation 1}{January 16, 2016} {
	Olumpus cellular was asked to tell them in real time every time Bronner’s cell phone was within five miles of specific addresses, and to provide every number he communicated with within ten miles of those addresses.
	Based on this investigation, the police focused their efforts on eight burner phones.
	8 days of daya without warrant, Olympus Cellular was convinced that safety and health of community were in danger.
	Bronner was switching burner phones, possibly justifying exigency.
}
\inv{Warrant 6}{January 25, 2016} {
	Track in real time, these eight cell phones, plus Bronner’s and DeNolf’s cell phones, whenever they were within five miles of the same ten adresses. They obtained the warrant within one day.
}
\inv{Warrant 7}{February 1, 2016} {
	All numbers contacted by or that contacted eight burners and Bronner and DeNolf’s phones. Olympus Cellular reported that the eight phones were no longer operational.
}
\inv{Informant}{February 2nd, 2016} {
	Comerford said that DeNolf was changing phones every week.
}
\inv{Warrantless Investigation 2}{February 3, 2015} {
	Instructed Olympus employees to provide them with all numbers contacted o contacted by Bronner’s new phone leading up to the Super Bowl.
}
\inv{Reports}{February 5-6, 2015} {
		On the 5th, Comerford said that the DeNolf operation wuld leave town for a prize fight
		On February 6th, there were two advertisements for human trafficking services with B.B. at the prize fight.
}
\inv{Warrantless Search 3}{February 7, 2015} {
	Every number contacted or contacted by Bronner between 12:00 and 10:00 pm and the current location within 2 miles of every one of these numbers. In addition, every number contacted by the 100 numbers ofund from that search. After concluding that 50 numbers were not connected to trafficking, law enforcement arrested 50 individuals; 40 clients and 10 associates. DeNolf was not arrested; bronner was arrested on February 9th.
}
\end{document}
