\documentclass[paper=letter,fontsize=10pt]{article}
\usepackage{newcent}
 
\usepackage{lineno}
\usepackage{enumitem}
\title{\textsc{\textit{Bronner v. Olympus} Issue 2 Brief}}
\newcommand{\case}[3]{\noindent {\large\textbf{\textit{#1}, #2 (#3)}} \par}
\newcommand{\inv}[3]{\noindent \textbf{#1} \\ \noindent \textit{#2} \begin{quote} #3 \end{quote} \par}
\date{}
\author{\textit{Varun Iyer} \hspace{.5em} $\cdot$ \hspace{.5em} \textit{August 3, 2019}}
\begin{document}
\maketitle
\inv{Interview 1}{February 9, 2016} {
	Chaney and Geesaman interviewed Andrea and Andy Sommerville. Both denied of allegations.
}
\inv{Rael’s Observations}{February 10, 2016} {
	Officer Rael had “grown worried” about Andy (but \textbf{not} about the safety of other students)\footnote{If Rael was concerned about ongoing safety, his observations would be less likely to be testimonial}.
	On that day, Andy was sullen and withdrawn and appeared to have been crying.
	Rael, \textbf{wearing his police uniform}, asked if Andy was okay and if he needed help, and Andy replied that he was fine.
}
\inv{Rael’s Observations}{February 11, 2016} {
	The next day, Andy appeared at Rael’s office. It was a casual, office-like setting with posters on the walls and no identification of authority. Andy asked if they could talk because something was bothering him. According to Rael, Andy described how he found child pornography in Bronner’s posession depicting his sister being raped.
	Andy asked what would happen after Bronner’s arrest, particularly whether he will go to jail.
	Officer Rael wrote down his recollections after the boy left. He called a counselor and the principal, but did not contact law enforcement officers.
	Chaney and Geesaman arrived two hours after this meeting.
	Officer Rael did not himself ask any questions.
}
\inv{Olympus Law}{}{
	Children must be at least ten years old in order to testify in Court. This legislation was intended to protect the physical and psychological well-being of victims under ten-years of age.
}

\inv{Andy Sommerville on Truth}{By the time of trial}{
	Sommerville has assisted his sister,Samantha, in practice for high school mock trial. Andy stated that he knows that lying is bad and that he believes that if he tells a lie, God will punish him for his sins.
}

\inv{Bronner’s Objection}{Trial}{
	Introduction of Rael’s testimony regarding his conversation were inadmissible hearsay without the opportunity for cross-examination.
}

\inv{Sasaki’s Testimony}{Trial}{
	Sasaki testified that he heard that Bronner possess child pornography.
}

\end{document}
